---
title: "Risk Mitigation Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable
---

```{r setup, include=FALSE}
library(flexdashboard)

# If needed run once from the Console
# install.packages("DT")
library(readr)
Risks <- read_csv("https://raw.githubusercontent.com/AlanBerg/LSAC-2018/cb65e9efba522b872615ec1bad682ec0d85cd89e/Groups/RiskMitigation/Risks.csv")
Websites <- read_csv("https://raw.githubusercontent.com/AlanBerg/LSAC-2018/master/Groups/RiskMitigation/URL.csv")
```

Overview 
=====================================  

### TOP TEN LIST


```{r child = 'Fragments/Description.md'}
```

### Key points to note

<span style="background-color:Plum;">**REF-3:**</span>{data-navmenu="High"}
=====================================  

### Description

### RISK Level

### Impact

### Mitigation


<span style="background-color:Plum;">**REF-2:**</span>{data-navmenu="Medium"}
=====================================  

### Description


### RISK Level

### Impact

### Mitigation

### Extra Resources


<span style="background-color:Plum;">**REF-3:**</span>{data-navmenu="Low"}
=====================================  

### Description

### RISK Level

### Impact

### Mitigation

### Extra Resources


Contact{data-navmenu="Help"}
===================================== 

### Information


Process {data-navmenu="Help"}
===================================== 

### Information

Searchable Library {data-navmenu="Library"}
===================================== 

### Search and print

```{r}
DT::datatable(Risks, extensions = 'Buttons',editable = TRUE, rownames = FALSE, options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```

Websites {data-navmenu="Library"}
===================================== 

### Intersting online sources

```{r}
DT::datatable(Websites, extensions = 'Buttons',editable = TRUE, rownames = FALSE, options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```



Resources {data-navmenu="Help"}
===================================== 

### Information



